Thermodynamic fragments in magic state theories

### 2021-02-15 appendix.tex
Full n-copy first elbow coordinates. Need to expand on the first elbow constraint
More code simplifications

\subsection{Binomial distributions and error bounds}\label{app:phi}
Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
\begin{align}	
	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
	&\text{for odd integers } \mmf\in[0,\nnf]. \label{eq:fn_app}
\end{align}
Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\dummy\in [1,\nnf-1]$,
	\begin{align}
		&\left[ 8\dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)} \leq \binom{\nnf}{\dummy} \leq \\
		&\left[ 2\pi \dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\dummy = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

\subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
The Wigner distribution of the $\NN$-copy qutrit maximally mixed state $\left(\id/3\right)\too{\NN}$ is the uniform distribution 
\begin{equation}\label{eq:wu}
	\W{\left(\id/3\right)\too{\NN}} = \Bigg( \overbrace{\frac{1}{9^\NN}, \dots, \frac{1}{9^\NN}}^{9^\NN} \Bigg).
\end{equation}
The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\noisys(\epsilon)$ in the unital fragment is a permutation of 
\begin{equation}\label{eq:wsu}
	\W{\noisys(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
\end{equation}
The two distinct components are plotted~\cref{fig:noisys} as a function of noise. 
It is clear that in the unital fragment the Strange state contains Wigner negativities in the regime $0 \leq \epsilon \leq \tfrac{3}{4}$.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{figs/noisys.pdf}
    \caption{\textbf{Wigner components of the noisy Strange state.} 
    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
    }
    \label{fig:noisys}
\end{figure}

The Wigner distribution of the $\NN$-copy $\epsilon$-noisy Strange state $\noisysN$ in the unital fragment is given by the convolution $\W{\noisysN} = \rm{W}_{\noisys(\epsilon)}\too{\NN}$.
In general, $\noisysN$ contains $\NN + 1$ distinct components, labelled $0,\dots, \NN$.
We present the distinct Wigner components of $\noisysN$ along with their multiplicites in~\cref{tab:lcsu}.
Note that LHS (RHS) refers to elbow coordinates $\ii$ on the left of and including (right of) the maximum, precisely
\begin{align}
&\text{LHS: } 0 \leq \ii \leq \left\lfloor \frac{\NN}{2} \right\rfloor ; \\
&\text{RHS: } \left\lfloor \frac{\NN}{2} \right\rfloor +1 \leq \ii \leq \NN.
\end{align}
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$\mlt_{\ii}(\NN, \epsilon)$} & \multicolumn{1}{|c}{$w_{\ii}(\NN, \epsilon)$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\
    & & RHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{2\ii+1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii-1}$ \\
    & & RHS & $8^{\NN-2\ii-1}\binom{\NN}{2\ii+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii+1}$ \\ \hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $8^{\NN-2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{\NN-2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2\ii}$ \\
    & & RHS & $8^{2\ii}\binom{\NN}{2\ii}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{\NN-2\ii}$ \\ \hline
  \end{tabular}
  \caption{Wigner components $w_{\ii}(\NN, \epsilon)$ of $\noisysN$ along with their multiplicities $\mlt_{\ii}(\NN, \epsilon)$ in decreasing order in $\ii,\ 0 \leq \ii \leq \NN$.
  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the parity of the components (LHS vs RHS).
  Multiplication $2\ii$ is considered modulo $(\NN+1)$.}
  \label{tab:lcsu}
\end{table}

For example, the distribution of state $\noisys(0)\too{2}$ is
\begin{equation*}
	\begin{split}
	\rm{W}_{\noisys(0)\too{2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
	\end{split}
\end{equation*}

Every standard Lorenz curve contains $\NN$ elbows, labelled by 
\begin{equation*}
\{(x_{\ii}, L_{\ii})\}_{\ii=-1,0,\dots,\NN}\ ,
\end{equation*}
where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$ are also included.
The maximum is the $(\lfloor \NN \rfloor/2)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
\begin{align}
	x_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^\NN\right), \\
	L_{\lfloor \NN \rfloor/2} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^\NN \right).
\end{align}
%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]

Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order and we present the elbow coordinates for standard Lorenz curves in~\cref{tab:lcsu_coord_elb_app}.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor \NN/2 \rfloor} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\lfloor \NN/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Standard Lorenz curves elbow coordinates.
  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $\NN$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
  }
  \label{tab:lcsu_coord_elb_app}
\end{table}

>>>>

\subsection{Binomial distributions and error bounds}\label{app:phi}
Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
\begin{align}	
	\Phi_+(af; nf, p) &\coloneqq \sum\limits_{\ell=0}^{af/2} \binom{nf}{2\ell} p^{2\ell} (1-p)^{nf-2\ell}, \nonumber\\ 
	&\text{for even integers } af\in[0,nf], \label{eq:fp_app} \\
	\Phi_-(af; nf, p) &\coloneqq \sum\limits_{\ell=1}^{(af-1)/2} \binom{nf}{2\ell+1} p^{2\ell+1} (1-p)^{nf-(2\ell+1)}, \nonumber\\ 
	&\text{for odd integers } af\in[0,nf]. \label{eq:fn_app}
\end{align}
Note that index $af$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\ell\in [1,nf-1]$,
	\begin{align}
		&\left[ 8\ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)} \leq \binom{nf}{\ell} \leq \\
		&\left[ 2\pi \ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\ell = 1,2, nf-1, nf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(af; nf, p) \geq \sum\limits_{\ell=0}^{af/2}\left[ 16\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
		&\text{2. } \Phi_+(af; nf, p) \leq \sum\limits_{\ell=0}^{af/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
		&\text{3. } \Phi_-(af; nf, p) \geq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd }af\in [1,nf] \\
		&\text{4. } \Phi_-(af; nf, p) \leq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd } af\in [1,nf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

\subsection{Standard Lorenz curve elbow coordinates}\label{app:lcsu_coord_elb}
The Wigner distribution of the $n$-copy qutrit maximally mixed state $\left(\id/3\right)^{\otimes n}$ is the uniform distribution 
\begin{equation}\label{eq:wu}
	\W{\left(\id/3\right)^{\otimes n}} = \Bigg( \overbrace{\frac{1}{9^n}, \dots, \frac{1}{9^n}}^{9^n} \Bigg).
\end{equation}
The Wigner distribution of the 1-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 
\begin{equation}\label{eq:wsu}
	\W{\rho_{\rm{S}}(\epsilon)} = \Bigg( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \Bigg)
\end{equation}
The two distinct components are plotted~\cref{fig:noisys} as a function of noise. 
It is clear that in the unital fragment the Strange state contains Wigner negativities in the regime $0 \leq \epsilon \leq \tfrac{3}{4}$.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{figs/noisys.pdf}
    \caption{\textbf{Wigner components of the noisy Strange state.} 
    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
    }
    \label{fig:noisys}
\end{figure}

The Wigner distribution of the $n$-copy $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ in the unital fragment is given by the convolution $\W{\rho_{\rm{S}}(\epsilon)^{\otimes n}} = \rm{W}_{\rho_{\rm{S}}(\epsilon)}^{\otimes n}$.
In general, $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ contains $n + 1$ distinct components, labelled $0,\dots, n$.
We present the distinct Wigner components of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicites in~\cref{tab:lcsu}.
Note that LHS (RHS) refers to elbow coordinates $i$ on the left of and including (right of) the maximum, precisely
\begin{align}
&\text{LHS: } 0 \leq i \leq \left\lfloor \frac{n}{2} \right\rfloor ; \\
&\text{RHS: } \left\lfloor \frac{n}{2} \right\rfloor +1 \leq i \leq n.
\end{align}
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$m_{i}(n, \epsilon)$} & \multicolumn{1}{|c}{$w_{i}(n, \epsilon)$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\
    & & RHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{2i+1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i+1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i-1}$ \\
    & & RHS & $8^{n-2i-1}\binom{n}{2i+1}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i-1}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i+1}$ \\ \hline
    \multirow{4}{*}{\raisebox{-4ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-1ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-2ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $8^{n-2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{n-2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{2i}$ \\
    & & RHS & $8^{2i}\binom{n}{2i}$ & $\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2i}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2i}$ \\ \hline
  \end{tabular}
  \caption{Wigner components $w_{i}(n, \epsilon)$ of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ along with their multiplicities $m_{i}(n, \epsilon)$ in decreasing order in $i,\ 0 \leq i \leq n$.
  The order changes depending on the noise level $\epsilon$, the parity of the number of copies $n$ and the parity of the components (LHS vs RHS).
  Multiplication $2i$ is considered modulo $(n+1)$.}
  \label{tab:lcsu}
\end{table}

For example, the distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$ is
\begin{equation*}
	\begin{split}
	\rm{W}_{\rho_{\rm{S}}(0)^{\otimes 2}} = \Bigg( &\overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64}, \\
	&\overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \Bigg)
	\end{split}
\end{equation*}

Every standard Lorenz curve contains $n$ elbows, labelled by 
\begin{equation*}
\{(x_{i}, L_{i})\}_{i=-1,0,\dots,n}\ ,
\end{equation*}
where the boundary points $(x_{-1}, L_{-1}) = (0,0)$ and $(x_{n}, L_{n}) = (1,1)$ are also included.
The maximum is the $(\lfloor n/2 \rfloor)$-th elbow and its coordinates are calculated by collecting all the positive Wigner components,
\begin{align}
	x_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left(1 + \left(\frac{7}{9}\right)^n\right), \\
	L_{\lfloor n/2 \rfloor} &= \frac{1}{2}\left (1 + \left(\frac{15 - 8\epsilon}{9}\right)^n \right).
\end{align}
%\sum_{j: even}^n a^j \binom{n}{j} = \frac{1}{2} [ (1+a)^n + (1-a)^n ]

Expressions for all the elbow coordinates follow from summing up the Wigner components in decreasing order and we present the elbow coordinates for standard Lorenz curves in~\cref{tab:lcsu_coord_elb_app}.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{i}$} & \multicolumn{1}{|c}{$L_{i}$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_-\left(2i;n,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{1}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ even}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_-\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$n$ odd}}} & LHS & $\Phi_+\left(2i;n,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2i;n,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\lfloor n/2 \rfloor} + \Phi_+\left(2i;n,\frac{8}{9}\right)$ & $L_{\lfloor n/2 \rfloor} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_+\left(2i;n,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Standard Lorenz curves elbow coordinates.
  The expresion depends on the noise level $\epsilon$, the parity of the number of copies $n$ and the location of the elbow relative to the maximum (LHS vs RHS).
  Multiplication $2i$ is considered modulo $(n+1)$.
  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{n}, L_{n}) = (1,1)$.
  }
  \label{tab:lcsu_coord_elb_app}
\end{table}

\subsection{Standard Lorenz curve coordinates}\label{app:lcsu_coord}
We can get explicit expressions for all $9^{n}$ points of the standard Lorenz curve $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes n}}{\id/3}$, in terms of the elbow coordinates:
\begin{align}
    x_{ij} &= \left( 1-\frac{j}{m_{i}} \right) x_{i-1} + \frac{j}{m_{i}} x_{i}, \label{eq:x}\\
    L_{ij} &= \left( 1-\frac{j}{m_{i}} \right) L_{i-1} + \frac{j}{m_{i}} L_{i} \label{eq:l}
\end{align}
for $j = 1,\dots,m_{i}$ and $i=0,\dots,n$, where multiplicities $m_i = m_i(n, \epsilon)$ are given in~\cref{tab:lcsu}.
